Asymptotic-Preserving Discretization of Three-Dimensional Plasma Fluid Models

### 2024-03-07 paper_version/main.tex
fix error in plotting eps

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{a4paper,scale=0.8}
\usepackage[square,numbers]{natbib}
\bibliographystyle{abbrvnat}
\usepackage{tikz}
\usepackage{tkz-euclide}
\usetikzlibrary{positioning, decorations.markings, arrows, intersections}
\usepackage{nicematrix}
\NiceMatrixOptions{cell-space-top-limit = 4pt}
\NiceMatrixOptions{cell-space-bottom-limit = 4pt}
\usepackage{tcolorbox}
\usepackage{caption, subcaption}
\captionsetup[figure]{labelfont={bf},name={Fig.},labelsep=period}
\captionsetup[table]{labelfont={bf},name={Tab.},labelsep=period}
\setlength\arrayrulewidth{0.7pt}
\usepackage{authblk}
\usepackage{soul}
%\usepackage{showlabels}
\usepackage{multirow}
\usepackage{comment}

@@

\begin{figure}
    \centering
    \includegraphics[scale=0.3]{paper_version/figures/primal_mesh.png}
    \hspace{1cm}
    \includegraphics[scale=0.3]{paper_version/figures/dual_mesh.png}
    \caption{Primal mesh (left) and dual mesh (right).}
    \label{fig:primal_dual_meshes}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=1.2]{z_axis_reduction.eps}
    \caption{Case I, $\lambda = 1$: Comparison of 1D two-fluid model and of 3D results (at
      time $t = 5 \times 10^{-4}$ projected onto the $z$-axis. The simulations were both
      conducted on meshes with 64 cells along the $z$-axis. No friction terms were taken
      into account. \review{The 3D result is generated under the setting in Fig.~2
  and restricted to the z-axis. They are slightly different from
  the 1D results possibly due to the impact of the outer boundary of the
  3D domain.}}
    \label{fig:z_axis_reduction}
\end{figure}

@@

                \draw[-to] (barycentric cs:_N1=1,_NE1=1,_N2=1,_NE2=1) to[out=90,in=0] ([shift={(-0.5,0.5)}]barycentric cs:_N1=1,_NE1=1,_N2=1,_NE2=1) node[left, gray] {Insulator};
                % Axes
                 \begin{scope}[shift={(6.5,-0.9)}]
                    \draw[blue, -to] (0,0) -- (20:0.7) node[right]{\small $z$};
                    \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
                    \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
                \end{scope}
            \end{tikzpicture}
        }
    \end{minipage}
    \hspace{1cm}
    \includegraphics[scale=0.2]{paper_version/figures/cube_mesh_primal.png}
    \hspace{1cm}
    \includegraphics[scale=0.2]{paper_version/figures/cube_mesh_dual.png}
    \caption{\review{Case II: domain sketch (left); primal mesh (middle); dual mesh (right).}}
    \label{fig:cube_domain_sketch}
\end{figure}

@@

In Fig.~\ref{fig:3d_vec_field_E_B_ue}, the numerical solutions for $\lambda = 1.0, 0.1$
and $0$ are shown to visualize the 3D structure of the electromagnetic field. Qualitative
verification can be done in many aspects. First, the rotational symmetry of the problem is
preserved. Second, the $\mathbf{E}$-field points from $\Gamma^+_C$ to $\Gamma^-_C$ with a
relatively uniform value of approximately 0.2
($=\text{applied voltage}/\text{cylinder length}$) as a consequence of the irrotational
$\mathbf{E}$-field in the steady state according to Faraday's law (which is also confirmed
in Fig.~\ref{fig:stabilization_comparison} \textbf{(b)}). Note that it does not hold for $\lambda = 1$
since the system has a large characteristic time and takes a long time to reach an
equilibrium, as will be shown later in Fig.~\ref{fig:origin-data_vs_time}. Besides, the
$\mathbf{B}$-field is azimuthal (vortex-shaped) and orthogonal to the
$\mathbf{E}$-field. Also, under the electric force, the electrons move towards the anode
$\Gamma^+_C$ as expected.
\begin{figure}
    \centering
    \begin{subfigure}[b]{\textwidth}
        \hspace{-1cm}
        \begin{tikzpicture}
        \draw[blue, -to] (0,0) -- (20:0.7) node[right]{\small $z$};
        \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
        \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
        \end{tikzpicture}
        \includegraphics[scale=0.2]{paper_version/figures/E-field_lambda-1.png}\hspace{0.6cm}
        \includegraphics[scale=0.2]{paper_version/figures/B-field_lambda-1.png}
        \includegraphics[scale=0.2]{paper_version/figures/electronVel_lambda-1.png}
        \caption{\colorbox{yellow!30}{$\lambda = 1.0$}}
    \end{subfigure}
     \begin{subfigure}[b]{\textwidth}
        \hspace{-1cm}
        \begin{tikzpicture}
        \draw[blue, -to] (0,0) -- (20:0.7) node[right]{\small $z$};
        \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
        \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
        \end{tikzpicture}
        \includegraphics[scale=0.2]{paper_version/figures/E-field_lambda-1e-1.png}
        \hspace{0.3cm}
        \includegraphics[scale=0.2]{paper_version/figures/B-field_lambda-1e-1.png}
        \includegraphics[scale=0.2]{paper_version/figures/electronVel_lambda-1e-1.png}
        \caption{\colorbox{yellow!30}{$\lambda = 0.1$}}
    \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
        \hspace{-1cm}
        \begin{tikzpicture}
        \draw[blue, -to] (0,0) -- (20:0.7) node[right]{\small $z$};
        \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
        \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
        \end{tikzpicture}
        \includegraphics[scale=0.2]{paper_version/figures/E-field_lambda-0.png}
        \hspace{0.3cm}
        \includegraphics[scale=0.2]{paper_version/figures/B-field_lambda-0.png}
        \includegraphics[scale=0.2]{paper_version/figures/electronVel_lambda-0.png}
        \caption{\colorbox{yellow!30}{$\lambda = 0.0$}}
    \end{subfigure}
    \caption{Case III: Snapshots of the $\mathbf{E}$-field, $\mathbf{B}$-field, and $\mathbf{u}_e$ for different $\lambda$ at $t = 0.5$. } 
    \label{fig:3d_vec_field_E_B_ue}
\end{figure}

@@

\begin{figure}
  \centering
    \includegraphics[scale=0.9]{data-vs-time_stepVoltage.eps}
    \caption{Case III: Time histories of quantities at the domain center and of the averaged current densities at $\Gamma^+_C$ (anode) and $\Gamma^-_C$ (cathode) for different values of $\lambda$. The simulations are done on a mesh with 1920 primal cells with 8 layers along the $z$-axis.}
    \label{fig:origin-data_vs_time}
\end{figure}

The stabilization proposed in Section~\ref{sec:reform-discrete} is essential to achieve
good results when $\lambda$ tends to zero. As is shown in
Fig.~\ref{fig:stabilization_comparison} \textbf{(a)}, the scheme without stabilization incurs a blow-up
when $\lambda$ is close to zero. The proposed stabilization clearly offers a remedy.
\begin{figure}
    \centering
\begin{minipage}[t]{0.4\textwidth}\centering
  \includegraphics[width=\textwidth]{stabilizationComparision_stepVoltage.eps}

  \parbox{0.9\textwidth}{\begin{tabular}[c]{ll}
    \textbf{(a)} & Time-dependent z-component of \\ & the $\mathbf{E}$-field
    in a boundary cell on $\Omega_N$
  \end{tabular}}
\end{minipage}%    
 \begin{minipage}[t]{0.6\textwidth}\centering
   \includegraphics[width=\textwidth]{data-vs-z_stepVoltage.eps}

@@

                \coordinate (S1) at ([shift={(-0.707,0.707)}]O1);
                \coordinate (S2) at ([shift={(-0.196,0.98)}]O2);
                \coordinate (P1) at ([shift={(0.707,-0.707)}]O1);
                \coordinate (P2) at ([shift={(0.196,-0.98)}]O2);
                \draw[violet] (S1) to[out=45, in=180 + 10] (S2);
                \draw[violet] (P1) to[out=45, in=180 + 10] (P2);
                \coordinate (SS1) at ([shift={({-0.707*1.5},{0.707*1.5})}]O1);
                \coordinate (SS2) at ([shift={({-0.196*1.5},{0.99*1.5})}]O2);
                \coordinate (PP1) at ([shift={({0.707*1.5},{-0.707*1.5})}]O1);
                \coordinate (PP2) at ([shift={({0.196*1.5},{-0.99*1.5})}]O2);
                \draw[very thick] (SS1) to[out=45, in=180 + 10] (SS2);
                \draw[very thick] (PP1) to[out=45, in=180 + 10] (PP2); 
                \draw[very thick] (SS2) to[out=-180+10, in=180+10] (PP2);
                \draw[very thick] (PP2) to[out=10, in=10] (SS2);
                \draw[violet] (S2) to[out=-180+10, in=180+10] (P2) to[out=10, in=10] (S2);
                \fill[red, opacity=0.2] (S2) to[out=-180+10, in=180+10] (P2) to[out=10, in=10] (S2);
                \draw[-to] ([shift={(3,1.5)}]SS1) to[out=90,in=0] ([shift={(-0.5,0.7)}]barycentric cs:SS1=1,SS2=1) node[left, gray] {Insulator};
                \node at (barycentric cs:P1=1,SS2=1) {Plasma};
            \end{tikzpicture}
        }
    \end{minipage}
    \hspace{1cm}
    \includegraphics[scale=0.2]{paper_version/figures/primal_mesh_bend.png}
    \hspace{1cm}
    \includegraphics[scale=0.2]{paper_version/figures/dual_mesh_bend.png}
    \caption{\review{Case IV: domain sketch (left); primal mesh (middle); dual mesh (right).}}
    \label{fig:bend_domain_sketch}
\end{figure}
\begin{figure}
    \centering
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[scale=0.3]{paper_version/figures/E-field_lamnbda-1_bend.png}\hspace{1cm}
        \includegraphics[scale=0.3]{paper_version/figures/B-field_lamnbda-1_bend.png}
        \caption{\colorbox{yellow!30}{$\lambda = 1$}}
    \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[scale=0.3]{paper_version/figures/E-field_lamnbda-0_bend.png}\hspace{1cm}
        \includegraphics[scale=0.3]{paper_version/figures/B-field_lamnbda-0_bend.png}
        \caption{\colorbox{yellow!30}{$\lambda = 0$}}
    \end{subfigure}
    \caption{Case IV: Snapshots of the $\mathbf{E}$-field and $\mathbf{B}$-field for different $\lambda$ at $t = 0.05$.}
    \label{fig:3d_vec_field_E_B_bend}
\end{figure}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{a4paper,scale=0.8}
\usepackage[square,numbers]{natbib}
\bibliographystyle{abbrvnat}
\usepackage{tikz}
\usepackage{tkz-euclide}
\usetikzlibrary{positioning, decorations.markings, arrows, intersections}
\usepackage{nicematrix}
\NiceMatrixOptions{cell-space-top-limit = 4pt}
\NiceMatrixOptions{cell-space-bottom-limit = 4pt}
\usepackage{tcolorbox}
\usepackage{caption, subcaption}
\captionsetup[figure]{labelfont={bf},name={Fig.},labelsep=period}
\captionsetup[table]{labelfont={bf},name={Tab.},labelsep=period}
\setlength\arrayrulewidth{0.7pt}
\usepackage{authblk}
\usepackage{soul}
%\usepackage{showlabels}
\usepackage{multirow}
\usepackage{comment}
%\usepackage[outdir=./]{epstopdf}

@@

\begin{figure}
    \centering
    \includegraphics[scale=0.3]{./figures/primal_mesh.png}
    \hspace{1cm}
    \includegraphics[scale=0.3]{./figures/dual_mesh.png}
    \caption{Primal mesh (left) and dual mesh (right).}
    \label{fig:primal_dual_meshes}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=1.2]{./figures/z_axis_reduction.eps}
    \caption{Case I, $\lambda = 1$: Comparison of 1D two-fluid model and of 3D results (at
      time $t = 5 \times 10^{-4}$ projected onto the $z$-axis. The simulations were both
      conducted on meshes with 64 cells along the $z$-axis. No friction terms were taken
      into account. \review{The 3D result is generated under the setting in Fig.~2
  and restricted to the z-axis. They are slightly different from
  the 1D results possibly due to the impact of the outer boundary of the
  3D domain.}}
    \label{fig:z_axis_reduction}
\end{figure}

@@

                \draw[-to] (barycentric cs:_N1=1,_NE1=1,_N2=1,_NE2=1) to[out=90,in=0] ([shift={(-0.5,0.5)}]barycentric cs:_N1=1,_NE1=1,_N2=1,_NE2=1) node[left, gray] {Insulator};
                % Axes
                 \begin{scope}[shift={(6.5,-0.9)}]
                    \draw[blue, -to] (0,0) -- (20:0.7) node[right]{\small $z$};
                    \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
                    \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
                \end{scope}
            \end{tikzpicture}
        }
    \end{minipage}
    \hspace{1cm}
    \includegraphics[scale=0.2]{./figures/cube_mesh_primal.png}
    \hspace{1cm}
    \includegraphics[scale=0.2]{./figures/cube_mesh_dual.png}
    \caption{\review{Case II: domain sketch (left); primal mesh (middle); dual mesh (right).}}
    \label{fig:cube_domain_sketch}
\end{figure}

@@

In Fig.~\ref{fig:3d_vec_field_E_B_ue}, the numerical solutions for $\lambda = 1.0, 0.1$
and $0$ are shown to visualize the 3D structure of the electromagnetic field. Qualitative
verification can be done in many aspects. First, the rotational symmetry of the problem is
preserved. Second, the $\mathbf{E}$-field points from $\Gamma^+_C$ to $\Gamma^-_C$ with a
relatively uniform value of approximately 0.2
($=\text{applied voltage}/\text{cylinder length}$) as a consequence of the irrotational
$\mathbf{E}$-field in the steady state according to Faraday's law (which is also confirmed
in Fig.~\ref{fig:stabilization_comparison} \textbf{(b)}). Note that it does not hold for $\lambda = 1$
since the system has a large characteristic time and takes a long time to reach an
equilibrium, as will be shown later in Fig.~\ref{fig:origin-data_vs_time}. Besides, the
$\mathbf{B}$-field is azimuthal (vortex-shaped) and orthogonal to the
$\mathbf{E}$-field. Also, under the electric force, the electrons move towards the anode
$\Gamma^+_C$ as expected.
\begin{figure}
    \centering
    \begin{subfigure}[b]{\textwidth}
        \hspace{-1cm}
        \begin{tikzpicture}
        \draw[blue, -to] (0,0) -- (20:0.7) node[right]{\small $z$};
        \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
        \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
        \end{tikzpicture}
        \includegraphics[scale=0.2]{./figures/E-field_lambda-1.png}\hspace{0.6cm}
        \includegraphics[scale=0.2]{./figures/B-field_lambda-1.png}
        \includegraphics[scale=0.2]{./figures/electronVel_lambda-1.png}
        \caption{\colorbox{yellow!30}{$\lambda = 1.0$}}
    \end{subfigure}
     \begin{subfigure}[b]{\textwidth}
        \hspace{-1cm}
        \begin{tikzpicture}
        \draw[blue, -to] (0,0) -- (20:0.7) node[right]{\small $z$};
        \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
        \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
        \end{tikzpicture}
        \includegraphics[scale=0.2]{./figures/E-field_lambda-1e-1.png}
        \hspace{0.3cm}
        \includegraphics[scale=0.2]{./figures/B-field_lambda-1e-1.png}
        \includegraphics[scale=0.2]{./figures/electronVel_lambda-1e-1.png}
        \caption{\colorbox{yellow!30}{$\lambda = 0.1$}}
    \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
        \hspace{-1cm}
        \begin{tikzpicture}
        \draw[blue, -to] (0,0) -- (20:0.7) node[right]{\small $z$};
        \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
        \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
        \end{tikzpicture}
        \includegraphics[scale=0.2]{./figures/E-field_lambda-0.png}
        \hspace{0.3cm}
        \includegraphics[scale=0.2]{./figures/B-field_lambda-0.png}
        \includegraphics[scale=0.2]{./figures/electronVel_lambda-0.png}
        \caption{\colorbox{yellow!30}{$\lambda = 0.0$}}
    \end{subfigure}
    \caption{Case III: Snapshots of the $\mathbf{E}$-field, $\mathbf{B}$-field, and $\mathbf{u}_e$ for different $\lambda$ at $t = 0.5$. } 
    \label{fig:3d_vec_field_E_B_ue}
\end{figure}

@@

\begin{figure}
  \centering
    \includegraphics[scale=0.9]{./figures/data-vs-time_stepVoltage }
    \caption{Case III: Time histories of quantities at the domain center and of the averaged current densities at $\Gamma^+_C$ (anode) and $\Gamma^-_C$ (cathode) for different values of $\lambda$. The simulations are done on a mesh with 1920 primal cells with 8 layers along the $z$-axis.}
    \label{fig:origin-data_vs_time}
\end{figure}

The stabilization proposed in Section~\ref{sec:reform-discrete} is essential to achieve
good results when $\lambda$ tends to zero. As is shown in
Fig.~\ref{fig:stabilization_comparison} \textbf{(a)}, the scheme without stabilization incurs a blow-up
when $\lambda$ is close to zero. The proposed stabilization clearly offers a remedy.
\begin{figure}
    \centering
\begin{minipage}[t]{0.4\textwidth}\centering
  \includegraphics[width=\textwidth]{./figures/stabilizationComparision_stepVoltage}

  \parbox{0.9\textwidth}{\begin{tabular}[c]{ll}
    \textbf{(a)} & Time-dependent z-component of \\ & the $\mathbf{E}$-field
    in a boundary cell on $\Omega_N$
  \end{tabular}}
\end{minipage}%    
 \begin{minipage}[t]{0.6\textwidth}\centering
   \includegraphics[width=\textwidth]{./figures/data-vs-z_stepVoltage}

@@

                \coordinate (S1) at ([shift={(-0.707,0.707)}]O1);
                \coordinate (S2) at ([shift={(-0.196,0.98)}]O2);
                \coordinate (P1) at ([shift={(0.707,-0.707)}]O1);
                \coordinate (P2) at ([shift={(0.196,-0.98)}]O2);
                \draw[violet] (S1) to[out=45, in=180 + 10] (S2);
                \draw[violet] (P1) to[out=45, in=180 + 10] (P2);
                \coordinate (SS1) at ([shift={({-0.707*1.5},{0.707*1.5})}]O1);
                \coordinate (SS2) at ([shift={({-0.196*1.5},{0.99*1.5})}]O2);
                \coordinate (PP1) at ([shift={({0.707*1.5},{-0.707*1.5})}]O1);
                \coordinate (PP2) at ([shift={({0.196*1.5},{-0.99*1.5})}]O2);
                \draw[very thick] (SS1) to[out=45, in=180 + 10] (SS2);
                \draw[very thick] (PP1) to[out=45, in=180 + 10] (PP2); 
                \draw[very thick] (SS2) to[out=-180+10, in=180+10] (PP2);
                \draw[very thick] (PP2) to[out=10, in=10] (SS2);
                \draw[violet] (S2) to[out=-180+10, in=180+10] (P2) to[out=10, in=10] (S2);
                \fill[red, opacity=0.2] (S2) to[out=-180+10, in=180+10] (P2) to[out=10, in=10] (S2);
                \draw[-to] ([shift={(3,1.5)}]SS1) to[out=90,in=0] ([shift={(-0.5,0.7)}]barycentric cs:SS1=1,SS2=1) node[left, gray] {Insulator};
                \node at (barycentric cs:P1=1,SS2=1) {Plasma};
            \end{tikzpicture}
        }
    \end{minipage}
    \hspace{1cm}
    \includegraphics[scale=0.2]{./figures/primal_mesh_bend.png}
    \hspace{1cm}
    \includegraphics[scale=0.2]{./figures/dual_mesh_bend.png}
    \caption{\review{Case IV: domain sketch (left); primal mesh (middle); dual mesh (right).}}
    \label{fig:bend_domain_sketch}
\end{figure}
\begin{figure}
    \centering
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[scale=0.3]{./figures/E-field_lamnbda-1_bend.png}\hspace{1cm}
        \includegraphics[scale=0.3]{./figures/B-field_lamnbda-1_bend.png}
        \caption{\colorbox{yellow!30}{$\lambda = 1$}}
    \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[scale=0.3]{./figures/E-field_lamnbda-0_bend.png}\hspace{1cm}
        \includegraphics[scale=0.3]{./figures/B-field_lamnbda-0_bend.png}
        \caption{\colorbox{yellow!30}{$\lambda = 0$}}
    \end{subfigure}
    \caption{Case IV: Snapshots of the $\mathbf{E}$-field and $\mathbf{B}$-field for different $\lambda$ at $t = 0.05$.}
    \label{fig:3d_vec_field_E_B_bend}
\end{figure}
